\documentclass[11pt]{article}

\usepackage{proposal}
\usepackage[margin=1in]{geometry}
\pagestyle{empty}

\begin{document}
\section*{Biographical Sketch: Aaron Dominguez}
\label{sec:bio}
\subsection*{Address}
Aaron Dominguez\\
Department of Physics and Astronomy\\
208 Jorgensen Hall\\
University of Nebraska at Lincoln\\
Lincoln, NE  68588-0299\\
+1 (402) 472-6016 office\\
+1 (402) 472-2879 fax\\
+41 76 487 55 43 CERN mobile\\
\href{mailto:aarond@unl.edu}{\texttt{aarond@unl.edu}}

\subsection*{Professional Preparation}
\begin{tabular}[c]{lll}
Whitman College                          & Math-Physics                     & 1992 BA\\
California Institute of Technology       & Applied Physics                  & 1992 BS\\
University of California at San Diego\ \ & Physics                          & 1994 MS\\
University of California at San Diego\ \ & Physics                          & 1998 PhD\\
\end{tabular}


\subsection*{Appointments}
\begin{tabular}[c]{lll}
University of Nebraska -- Lincoln          & Associate Professor of
Physics & 2009-present \\
University of Nebraska -- Lincoln          & Assistant Professor of
Physics & 2004-2009 \\
Lawrence Berkeley National Laboratory\ \ & Postdoctoral Researcher & 1999-2004\\
University of California at San Diego\ \ & Postdoctoral Researcher & 1999
\end{tabular}

\subsection*{Publications}
\textit{Recent publications:}
\begin{enumerate}
\item R. Adolphi,\ldots\textbf{A.~Dominguez}  \textit{et al.} [CMS Collaboration], ``The CMS
  experiment at the CERN LHC,'' JINST \textbf{3}, S08004 (2008)
\item \textbf{A.~Dominguez}, ``The CMS pixel detector,'' NIM A
  \textbf{581}, 343 (2007)
\item \textbf{A.~Dominguez}, I.~Iashvili, S.~Willenbrock (editors),
  ``Tevatron-for-LHC Report: Higgs,'' Fermilab publication (2006), see
  \url{http://conferences.fnal.gov/tev4lhc} and \href{http://arxiv.org/abs/hep-ph/0612172}{hep-ph/0612172}.
%\item%{Acosta:2005ga}
%  D.~Acosta,\ldots\textbf{A. Dominguez} \textit{et al.}, % CDF
%  ``Search for Higgs bosons decaying into $b\bar{b}$ and produced in  association with a vector boson in $p\bar{p}$ collisions at $\sqrt{s} =
%1.8$ TeV,'' Phys.\ Rev.\ Lett.\  {\bf 95}, 051801 (2005)
\item V.M.~Abazov, \ldots\textbf{A. Dominguez} \textit{et al.},
  ``Search for Higgs Boson Production in Dilepton and Missing Energy
  Final States with 5.4\fb of $p\bar{p}$ Collisions at
  $\sqrt{s}=1.96\TeV$,'' Phys.\ Rev.\ Lett. \textbf{104}, 061804 (2010).
\item D.~Acosta,\ldots\textbf{A. Dominguez} \textit{et al.}, % CDF
  ``Measurement of the tt-bar Production Cross Section in p anti-p
  Collisions at $\sqrt{s}=1.96\TeV$ using Lepton + Jets Events with
  Secondary Vertex b-tagging,'' Phys.\ Rev.\ D {\bf 71}, 052003 (2005).

\end{enumerate}

% \vspace{0.5in}

% \textit{Others:}
% \begin{enumerate}

% \item \textbf{Thesis of D.~A.~M.~Dominguez,} ``Search for neutral Higgs bosons in electron
%   positron interactions at center-of-mass energies between $130\mathrm{\ Ge\kern
% -0.1em V}$ and $183\mathrm{\ Ge\kern -0.1em V}$,'' UMI-99-07602

% \item M.~Acciarri {\it et al.}, % [L3 Collaboration]
% ``Higgs candidates in $e^+e^-$ interactions at $\sqrt{s} = 206.6\mathrm{\ Ge\kern
% -0.1em V}$,''
% Phys.\ Lett.\ B {\bf 495}, 18 (2000)
% [arXiv:hep-ex/0011043]
% %\\{}CERN-EP-2000-140
% %\href{http://www.slac.stanford.edu/spires/find/hep/www?eprint=hep-ex\%2F0011043}{SPIRES entry}

% \item O.~Dubois, O.~Ganel, R.~Wigmans, W.~Brower, A.~Dominguez, C.~Duba and
% H.~Paar,
% ``Beam Test Results From The Spakebab Electromagnetic Calorimeter,''
% Nucl.\ Instrum.\ Meth.\ A \textbf{368}, 640 (1996).

% \item%{Acciarri:2000ty}
%   M.~Acciarri {\it et al.}, %  [L3 Collaboration]
%   ``Search for charged Higgs bosons in $e^+e^-$ collisions at
%   centre-of-mass energies up to $202\mathrm{\ Ge\kern
% -0.1em V}$''
%   Phys.\ Lett.\ B {\bf 496}, 34 (2000)
%   [arXiv:hep-ex/0009010]

% \item%{Acciarri:2000zp}
%   M.~Acciarri {\it et al.}, %  [L3 Collaboration]
%   ``Search for a Higgs boson decaying into two photons in $e^+e^-$
%   interactions at $\sqrt{s} = 189\mathrm{\ Ge\kern
% -0.1em V}$,''
%   Phys.\ Lett.\ B {\bf 489}, 115 (2000)
% [arXiv:hep-ex/0008025]
% %\\{}CERN-EP-2000-103
% %\href{http://www.slac.stanford.edu/spires/find/hep/www?eprint=hep-ex\%2F0008025}{SPIRES entry}


% \end{enumerate}

\subsection*{Synergistic Activities and Recent Awards}
\begin{itemize}
%\item Lecturer at Bright Lights ``Get Wired with PrairieFire''
%  workshop at UNL, July 11, 2005
\item Co-convenor of Higgs section of TeV4LHC workshop 2004-2006.  See
  \url{http://conferences.fnal.gov/tev4lhc} for more information
  about the conference
\item Founder and first director of the BEST (Bilingual
  English/Spanish Tutors) program in Aurora, IL and now in Lincoln, NE
\item Parents Recognition Teaching Award, UNL, 2006.
\end{itemize}

\subsection*{Collaborators and Other Affiliations}
The DZERO Collaboration consists of 562 physicists from 78 institutions.
The collaboration members are listed on the DZERO web page,
\url{http://www-d0.fnal.gov/~madaras/authorlist.html}

\noindent The CMS Collaboration consists of 2078 physicists from 165
  institutions. The collaboration members are listed on the CMS web page,
\href{http://cmsdoc.cern.ch/cms.html}{http://cmsdoc.cern.ch/cms.html}.

\subsection*{Thesis Adviser and Postdoctoral Sponsors}
\begin{itemize}
\item Ph.D. Adviser: Professor James Branson, University of California
  at San Diego
\item Postdoctoral Sponsors: Professor James Branson; Dr. Angela
  Galtieri, Lawrence Berkeley National Laboratory
\end{itemize}

\newpage{}
\section*{Aaron Dominguez: Grants Awarded and Pending}
\begin{itemize}
\item Grants awarded 2011/2012
  \begin{itemize}
  \item NSF: ``Any Data, Anytime, Anywhere.'' Co-PIs: Kenneth Bloom;
    David Swanson and others. Senior Personnel: Aaron Dominguez and
    others. \$710k
  \item NSF: ``U.S. CMS Operations at the LHC'' PI: Daniel Marlow.
    Senior Personnel: Aaron Dominguez and others.  \$10M for 5 years.
  \end{itemize}
\item Grants awarded 2010/2011
  \begin{itemize}
  \item NSF: ``Searching for and Discovering New Physics at the Large
    Hadron Collider, the Tevatron, and in Cosmic Rays'' PI: Kenneth
    Bloom, Co-PI's Aaron Dominguez, Dan Claes, Ilya Kravchenko,
    Gregory Snow, \$2M over three years
  \end{itemize}
\item Grants awarded 2009/2010
  \begin{itemize}
  \item NSF: ``MRI-R2: Development of a Pixel Detector for the
    Upgraded CMS Experiment,'' PI: Alice Bean, Co-PI's Aaron
    Dominguez, Cecilia Gerber, Timothy Bolton, Karl Ecklund, Angel
    Lopez, \$1.7M over three years
  \end{itemize}
\item Grants awarded 2008/2009
  \begin{itemize}
  \item NSF: Supplement to ``PIRE'' grant (see below) for postdoctoral
    researcher to be stationed at PSI in Switzerland. PI: Aaron
    Dominguez, \$150k/yr for two years.
  \end{itemize}
\item Grants awarded 2006/2007
  \begin{itemize}
  \item NSF: ``PIRE: Collaborative research with the Paul Scherrer
    Institute and Eidgenoessische Technische Hochschule on Advanced
    Pixel Silicon Detectors for the CMS detector,'' PI: Alice Bean,
    Co-PI's Aaron Dominguez, Cecilia Gerber, Timothy Bolton, Angel
    Lopez, \$2.5M over five years
  \end{itemize}
\item Grants awarded 2005/2006
  \begin{itemize}
  \item NSF ``CAREER: Superior Silicon Tracking and Discovery at CMS and
    D0,'' PI Aaron Dominguez, \$550k over 5 years.
  \item Fermilab: ``Using Pixel Clusters to Form Track Stubs: Proposal for a Summer
LPC Project.'' PI Aaron Dominguez. \$15.5k for the summer of 2006.
  \end{itemize}
\item Grants awarded 2004/2005
  \begin{itemize}
  \item ``Proposal for Tier-2 US~CMS Site at UNL.'' PI: David
    R.~Swanson. Co-PIs: Kenneth Bloom; Aaron Dominguez.
    Collaborators: Daniel Claes; Makoto Furukawa; Carl Lundstedt;
    Gregory Snow.  \$2M over 5 years  
  \item ``Nebraska EPSCoR FIRST AWARD: Particle Physics at the
    Tevatron and LHC.'' PI Aaron Dominguez, \$20k for one year
  \end{itemize}
%\item Grants pending 2007/2008
%  \begin{itemize}
%  \item Research Corporation Cottrell Scholar: ``Silicon Pixel
%    Detectors and the BEST Tutoring Program.'' PI: Aaron Dominguez, \$100k.
%  \item DOE: Outstanding Junior Investigator Award ``CMS Pixel Detector
%    Construction and R\&D,'' PI: Aaron Dominguez, \$220k.
%  \item Internet2: ``IDEA Application: Deployment of production-use
%    dynamic circuit capabilities for LHC high-impact data movement,''
%    application for innovation award.
%  \end{itemize}
% \item Grants pending 2004/2005
%   \begin{itemize}
%   \item ``Experimental Particle Physics at the Tevatron and LHC,'' NSF
%     Proposal \#0456674.  PI's: Kenneth Bloom; Aaron Dominguez
% %  \item ``Discovery Through Superior Silicon Tracking,'' DOE
% %    Outstanding Junior Investigator Award. PI: Aaron Dominguez
%   \item  ``Building EPSCoR -- State/National Laboratory Partnerships:
%     Preparations for Physics Discovery at the Large Hadron Collider.''
%     PI Kenneth Bloom, co-PI Aaron Dominguez
\end{itemize}


% \include{research_background}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
