\section{Research projects for IRES participants}
\label{sec:projects}

As previously mentioned, the construction of the Phase~1 upgrade to
the CMS pixel detector will be shared among groups from Europe and the
United States.  The innermost layers of the barrel pixel detector will
be built by the Swiss consortium of PSI, ETHZ and the University of
Zurich, who are recognized for their expertise in pixel detector
design and construction.  The United States is responsible for the
forward pixel detector construction.  The design of this new upgrade
has been done in such a way as to minimize the differences in
components needed for the forward versus barrel detectors.  The hybrid
modules used for the forward and barrel detectors are essentially the
same, for example.  This proposal aims to continue building the bridge
between these Swiss and US groups through an exchange of expertise in
pixel detector design, testing, characterization and construction.

The US students placed at ETHZ will be working with our Swiss
colleagues on the following projects during stays of approximately
three to eight months after which they will return to their home institutions
bringing with them the skills and knowledge gained.
\begin{itemize}
\item Test beams
  \begin{itemize}
  \item Pre-production detector modules will be studied in test beams
    at PSI, Fermilab and other facilities
  \item Track reconstruction efficiencies and resolutions will be
    measured
  \item The performance of the detector will also be validated in high
    rate data taking similar to what will be present in the inner
    regions of CMS during high luminosity operations of the LHC
  \end{itemize}
\item Radiation hardness tests
  \begin{itemize}
  \item Both the readout chip and the sensor have been designed to be
    tolerant of harsh radiation environment of the LHC
  \item These rad-hard design principals need to be verified and
    characterized by comparing the pre and post-irradiation
    performance in test beams and on the bench
  \end{itemize}
\item Module test procedures
  \begin{itemize}
  \item Building on previous experience doing something similar to
    what was done for the current pixel detector, detailed procedures
    to characterize the performance of the pixel modules need to be performed
  \item The intrinsic noise of the readout chip plus sensor
    combination will be measured
  \item The procedure called ``trimming'' to normalize all pixel
    thresholds across the readout chip to the same value will be
    optimized to ensure the lowest thresholds possible
  \item High rate performance of the system will be validated with
    x-ray test stands.
  \item These same x-ray stands can also be used to produce
    mono-energetic x-rays to be used for energy calibrations of the
    readout chip
  \end{itemize}
\end{itemize}

The research plan for the students will be well integrated in the
overall CMS Phase 1 upgrade work, and the Swiss senior personnel has
committed to identify projects for each students appropriate in scale
and complexity. Each of the students will be assigned his or her
individual project. The projects listed above have a unified research
theme revolving around different aspects of physics and performance of
silicon sensors and readout, ensuring the cohort experience for the
IRES participants. It is expected that the students will work in the
same lab on projects that are similar enough to facilitate discussion
among the students and sharing of knowledge and skills. 

At ETHZ, the students will be mentored and guided by the Swiss faculty
and senior researchers, and supervised by a U.S. post-doc stationed
there.  The mentoring faculty from the U.S. institutions and the Swiss
side will regularly meet and discuss the progress with the projects
and the performance of each student.  Upon completion of their visit,
the students will return to continue these activities at the home
institutions.  The expertise the students will acquire working with
the leading Swiss pixel detector experts, and familiarity with the
test stands and electronic equipment specifically developed for the
Phase~1 Pixel Detector, will be of great use in setting up and running
analogous kinds of projects at their Universities.
% Students supervised by a US postdoc at ETHZ will collaborate with our
% Swiss colleagues on the projects outlined above and will then return
% home to continue such activities at the home institutions.  
The goal is to build teams of new pixel detector experts and to
transition from construction to installation and commissioning of the
new detector after the funding cycle of this grant is finished.

The tangible outcome for the students themselves, in addition to
acquiring new skills and knowledge, as well as experience in
conducting research with international partners, will be the "hardware
chapter" in the Ph.D. thesis for doctoral students, or a M.S. thesis
for students pursuing the M.S. degree. It is expected that the results
of the R\&D within the pixel upgrade project, including the
contribtion from IRES participants, will be published in the Nuclear
Instruments and Methods in Physics journal, as well as presented at
international conferences. The IRES participants will be included in
the author lists.
